### 2021-04-23 input/experiments.tex
mostly implemand algo + transi xpe to related work

Figure~\ref{fig:geant} shows the results of this experimentation. The
top part corresponds to the one source experiment, while the bottom
part corresponds to the one source per cluster experiment.

@@

\noindent Figure~\ref{fig:geant} shows that, when adding the
inter-continental link again, the two clusters can communicate
again. In the experiment involving one source for two clusters, it
generates traffic. After a $200$ milliseconds delay corresponding to
the new link latency, the cut off cluster starts to communicate
$\alpha$ messages again. Eventually, all \processes belong to the same
partition. However, in the experiment involving one source \emph{per}
cluster, the new link does not trigger noticeable traffic, for
\processes already know their closest source located in their
respective cluster.

@@

>>>>

Figure~\ref{fig:geant} shows the results of this experimentation. The
top part displays the one source experiment while the bottom part
displays the one source per cluster experiment.

@@

\noindent Figure~\ref{fig:geant} shows that, when adding the
inter-continental link again, the two clusters can communicate
again. In the experiment involving one source for two clusters, it
generates traffic. After a $200$ ms delay corresponding to
the new link latency, the cut off cluster starts to communicate
$\alpha$ messages again. Eventually, all \processes belong to the same
partition. However, in the experiment involving one source \emph{per}
cluster, the new link does not trigger noticeable traffic, for
\processes already know their closest source located in their
respective cluster.

@@

Next Section reviews state-of-the-art approaches for content indexing
in geo-distributed infrastructures and explains their shortcomings in
such context.

### 2021-04-23 input/proposal.tex
mostly implemand algo + transi xpe to related work

This vector of versions constitutes a summary of deliveries. \NAME
uses it to detect possible inconsistent partitioning as depicted in
Figure~\ref{fig:proofB}. A detecting \process then propagates a
$\delta$ message conveying the unique identifier $s$ and version $c$
of the partition along with a path $\pi$ comprising the identity of
\processes that forwarded the corresponding $\alpha$ message. Such
$\delta_{s, c}^{\pi}$ message implements the uncertain $\delta?$ message
of Figure~\ref{fig:proofB}. It fulfils the double role of removing
stale control information without modifying the local counter of the
source (since the partition may still exist), and removing loops to
ensure termination (since \processes do not modify their local state
to reflect such delivery, messages piggyback monotonically such
increasing control information). Thus, $\delta$ messages used in
Propagation~I' are more efficient both in propagation time and
traffic, for they propagate using every communication link available
in the partition, and they do not need to carry their path.
Fortunately, Propagation~I' happens more often than Propagation~IV.
Yet, \processes that belong to a partition need to save the path taken
by the corresponding $\alpha$ messages to enable Propagation~IV.  In
the worst case, the path includes every \processes in the system but
converges in average to the average diameter of partitions. Thus,
message paths and \NAME have an interesting synergy: Paths tend to be
smaller as the number of sources in the system increases. Bloom
filters could introduce another trade-off by further decreasing the
size of path data structures at the cost of premature stopped
propagation that could impair consistent
partitioning~\cite{whitaker2002forwarding}.

>>>>

This vector of versions constitutes a summary of deliveries. \NAME
uses it to detect possible inconsistent partitioning as depicted in
Figure~\ref{fig:proofB}. A detecting \process then propagates a
$\delta$ message conveying the unique identifier $s$ and version $c$
of the partition along with a path $\pi$ comprising the identity of
\processes that forwarded the corresponding $\alpha$ message. Such
$\delta_{s, c}^{\pi}$ message implements the uncertain $\delta?$
message of Figure~\ref{fig:proofB}. It fulfils the double role of
removing stale control information without modifying the local counter
of the source (since the partition may still exist), and removing
loops to ensure termination (since \processes do not modify their
local state to reflect such delivery, messages piggyback monotonically
such increasing control information).

$\delta_{s, c}$ messages used in Propagation~I' are more efficient
than $\delta_{s, c}^\pi$ messages used in Propagation~IV, both in
propagation time and traffic. First, the former propagate using every
communication link available in the partition, while the latter
propagate following the dissemination tree of the corresponding
$\alpha$ to purge. Second, the former only piggyback source and
counter while the latter piggyback the path taken by the corresponding
$\alpha$ to purge.  In the worst case, a path includes every
\processes in the system but converges on average to the average
diameter of partitions. Nevertheless, message paths and \NAME
synergyze with each other: Paths tend to be smaller as the number of
sources in the system increases. Bloom filters could introduce another
trade-off by further decreasing the size of path data structures at
the cost of premature stopped propagation that could impair consistent
partitioning~\cite{whitaker2002forwarding}.
